Followers Are Not Enough: A Multifaceted Approach to Community Detection in Online Social Networks

### 2014-11-30 paper-postreview/response-to-editor.txt

- "However, this approach focused on data for a particular topic...": this is not a credible justification to dismiss the work. The fact that you present an approach based on structure together with this one does not represent a significant contribution per se in my opinion.

* See the previous response.

- "For this reason, we coarsen each time series by considering non-overlapping time intervals...": this time series might be rather sparse. A discussion of this issue might be helpful.

* The resultant time series were indeed rather sparse, but this sparsity accurately reflects the usage statistics we were trying to capture. As users are not constantly tweeting, the activity profiles, and any coarsening of such an activity profile, should reflect this. We appreciate this comment and completely agree that this discussion would be helpful and added a few sentences to discuss this issue in section 2.3 where we first introduced the binning procedure.

@@

- "A positive value for the transfer...": this is just an assumption, you should say that you assume this.

* We have revised the manuscript to emphasize the property that immediately follows from the definition of transfer entropy, rather than an assumption that we have made. We admit that in the prior version our interpretation of the positivity was just an assumption, and we have performed significant refactoring of all of this work to make our interpretation more concrete in the revised manuscript. The assumption of positivity now is 100% the mathematical definition of a reduction in uncertainty and we now imply no further result such as influence or causality. Thank you for the suggestion.

@@

- In general, the 3 metrics listed in (2), (3) and (4) are not properly motivated in my opinion.

* Thank you for this comment. We expanded section 2.4 in the revised manuscript in order to motivate more in details these metrics.

- Section 2.5: the extraction of the weights is pretty standard, I do not consider this as a contribution per se.

* As noted in previous responses, the scope of this paper was not to present new weighting metrics, but rather to illustrate the importance of using *several* standard weighting metrics in order to extract several communities from a real-world online social network.

@@

*

- Figure 2: I cannot se real insights from these plots.

*

- For meaningful community structure...:: It is not clear to me why this should be the case. You can have in theory similar communities. This is probably not the case, but you should avoid to say that you expect this behavior.

@@

- "Similarly, for the coverings corresponding to...": it is not possible to compare these results directly, since they represent very different properties. They are not really normalized/scaled up.

*

- "This means that these accounts had high influence...": this is a strong claim. This might be simply due to the higher probability of retweet for that account, i.e., the use of the entropy transfer function might not necessary. The actual introduction of such a complex tool for describing this tool is not completely justified.

and 
- "Lastly, it is interesting to note...": the same might be true for these accounts.

* As has been stated in previous responses the manuscript has been significantly refactored to not assume the implication of either influence or causality but simply use transfer entropy as a mathematical tool to quantify activity-based predictive capacity, which we define explicitly in the revised paper. While we tried to make it clear in the original manuscript that we were hesitant as whether this was truly a measure of social influence, the reviewers comments illustrated to us that we had not done this well enough. We hope that this refactoring of the paper makes this skepticism as well as our actual intentions with this method more clear.

@@

- "even activity-based influence": it depends, you can consider weights accordingly, for example based on the frequency/intensity of the interaction, etc. You can even add a weight using Granger correlation. You can put a weight if the correlation is higher than a certain given threshold for example - and only tnen apply the community detection algorithm.

* We agree. Alternative activity-based metrics could and should certainly be applied. In this sentence, we meant to emphasize that the structural network alone would not capture this information, and therefore performing influence detection using this network might lead to more accurate influence measures. We have added some sentences discussing and hopefully making this more clear.

- "erroneous results": how can you say that your results are corrects.

### 2014-11-30 paper-postreview/response-to-editor.txt

- In particular, as far as the activity-based approach is concerned, the definition of influence is very difficult to justify. The method itself is not particularly new. It was used in the past in [44]. In general, in my opinion, the use of transfer entropy for measuring the influence of a certain user on another user is fairly questionable. In fact, saying that a certain user influences another one considering th patterns of user activity might be rather questionable. What about different "followees" influencing the same person? What about external influences? In any case, I think that it is difficult to talk about "influence" in these cases. And then there is a fundamental question: it is not clear which information you can get using transfer entropy and its semantics.

* The method used in [44] is very different from our own. We originally cited this paper because it was the impetus for us considering point process-type models of user behavior in social media, but we see that this may have been misleading. The method in [44] assumes a weighted adjacency matrix based on the point-wise (in time) informational coherence between any two nodes in the network. The informational coherence is computed as the normalized mutual information between the marginal causal states associated with each node in the vertex, and thus measures whether or not the information processing between any two nodes is associated across time. Thus, this measure is neither directed, nor does it account for lagged effects in terms of the interaction between two nodes in network, as our method does.
(Elisa: I think this answers only the very first part of the comment. Josh, could you please elaborate also on the rest (I leave this to you since it's the transfer entropy stuff))

- Also, the similarity based on topics is not a contribution per se in my opinion. Topic extraction techniques (also in more refined ones, as cited by the authors) have been used in several papers.

* Aside from he activity-based weighting. We do not believe that the contribution of our paper is any of the particular weightings, but rather that using them all in parallel provides a deeper analysis of the complex community structure present in online social networks.  We sought to include simple, reasonable metrics motivated by the interaction-, topic-, and activity-based questions, in order to unveil the multifaceted communities present in these networks, but we did not intend for these to be new. We have rewritten several of the sections of the paper to emphasize this change. We have also re-titled the paper and completely rewritten the abstract to emphasize that the contribution is in the multifaceted approach not in the particular weightings. We hope this is now more clear.

@@

- "However, with the prevalence of large rich data sets for online social networks": I think that the opposite is actually true. Sociologists usually go beyond simple structure and/or structure is used to describe dynamics.

* We did not mean to claim that sociologists currently take this approach, but rather that this approach was more reasonable in the era of small-scale studies of human/human interaction (for example, the small-world experiment of Stanley Milgram, or Zachary's Karate club).

- "Interaction-based": why is this different from activity based? It seems to me that this is a sort of limit case of the "activity-based" considering a simplification of the problem: communication vs no communication.

* This is a very interesting point, while the interaction based and activity based will have *some* overlap they are not the same and not really a limiting case either. Consider the case where a person tweets in reaction to an individuals tweet but does not mention nor retweet the original user. This would be detected in the activity based but not the interaction based. You may also consider the case where a community is all tweeting about a particular event as that event is occurring but not actually talking to each other, this would register in the topic based and activity based but not in the interaction based.   In the revised manuscript we provided concrete examples, from the experimental network, of both of these circumstances. We hope that this addition to the manuscript will help clear up this confusion.

@@

- "We divide our approaches into four categories": I think that this is not strictly necessary since you have already mentioned this.

* Thank you for this suggestion. We have revised the manuscript to remove this redundancy.

- "However, we conjecture": rightly, the authors say that this is just a conjecture. At the same time, very bold claims are based on this very simple conjecture.

* We agree that our original presentation of transfer entropy did not do a good enough job of stressing the difference between social and information theoretic influence. We have completely refactored our presentation of transfer entropy to make it more clear exactly what we believe transfer entropy does and does not capture in the setting of our paper.

@@

*

- "This means that these accounts had high influence...": this is a strong claim. This might be simply due to the higher probability of retweet for that account, i.e., the use of the entropy transfer function might not necessary. The actual introduction of such a complex tool for describing this tool is not completely justified.

and 
- "Lastly, it is interesting to note...": the same might be true for these accounts.

* The manuscript has been significantly refactored to not assume the implication of either influence or causality but simply use transfer entropy as a mathematical tool to quantify activity-based predictive capacity, which we define explicitly in the revised paper. While we tried to make it clear in the original manuscript that we were hesitant to whether this was truly a measure of social influence, the reviewers comments illustrated to us that we had not done this well enough. We hope that this refactoring of the paper makes this skepticism as well as our actual intentions with this method more clear.

@@

* We have expanded on this point in the revised manuscript, and given examples of how influence detection based solely on the structural network could result in an incomplete understanding of the influence exhibited by users in an online social network.

Reviewer 2
==========

- My only minor complaint is the following. Depending on the "type" of links considered, I expect the network to be different. Why did the authors focus only on communities, instead of considering also more basic network properties? I would add some statistics about it.

* Thank you for this suggestion. We decided to focus the paper on communities, and felt that going into more detail about the differences in other network properties went beyond the scope of our analysis. However, as we indicated in the revised Future Work section, we believe that such investigations could yield new insights into the multifaceted nature of online social networks and we do intend to do this analysis, but we believe this would be more appropriate for a separate paper.

### 2014-11-30 paper-postreview/intro.tex

Studying how the communities derived from follower-followee, activity-based, topic-based, and interaction-based networks are disjoint as well as overlapping allow for a more complete picture of the \emph{implicit} networks present in online social media, as opposed to the \emph{explicit} social network indicated by follower links alone. In this paper, we explore the relation between these various possible networks through their corresponding communities. We begin by describing the methodologies used to generate the various types of networks, and infer their community structure.  We then explore how the communities of users differ depending on the type of network used. \sout{\emph{Finally, we explore how communication patterns differ across and within the different community types. (Elisa: We do that?)}} We conclude by illustrating that this multifaceted question-oriented approach to community detection provides interesting insights into the intricate multifaceted structure of several different users' communities, information that would not be available if only a single form of community detection was performed. 
%\section{Related Work}

>>>>

Studying how the communities derived from follower-followee, activity-based, topic-based, and interaction-based networks are disjoint as well as overlapping allow for a more complete picture of the \emph{implicit} networks present in online social media, as opposed to the \emph{explicit} social network indicated by follower links alone. In this paper, we explore the relation between these various possible networks through their corresponding communities. We begin by describing the methodologies used to generate the various types of networks, and infer their community structure.  We then explore how the communities of users differ depending on the type of network used.
%\sout{\emph{Finally, we explore how communication patterns differ across and within the different community types. (Elisa: We do that?)}} 
We conclude by illustrating that this multifaceted question-oriented approach to community detection provides interesting insights into the intricate multifaceted structure of several different users' communities, information that would not be available if only a single form of community detection was performed. 
%\section{Related Work}
